\documentclass{resume}
\usepackage{hyperref}
\usepackage{multirow}
\pagenumbering{gobble}

\begin{document}

\filcenter{\textbf{Anirudhan J. Rajagopalan}}\\

\noindent{\href{http://rajegannathan.in}{http://rajegannathan.in} \hfill \href{https://github.com/rajegannathan}{https://github.com/rajegannathan}}\\
\noindent{\href{mailto:anirudhan@rajegannathan.in}{\nolinkurl{anirudhan@rajegannathan.in}} \hfill \href{https://www.linkedin.com/in/rajegannathan}{https://www.linkedin.com/in/rajegannathan}}\\
\noindent{+1-- (646)-436 -3808 \hfill \href{http://stackoverflow.com/users/846970/anirudhan-j}{http://stackoverflow.com/users/846970/anirudhan-j}}
\section{Education}
\subsection[Master of Science, Computer Science]{\textsc{Master of Science, Computer Science} \hfill \textbf{3.82}}%
\small{Courant Institute of Mathematical Sciences} \hfill \small{Dec, 2016}
  \begin{description}
    \item{Course List:} \small{\textit{Deep Learning, Computational Machine Learning, Foundations of Machine Learning, Web Search Engines, Realtime \& Bigdata Analytics, Fundamental Algorithms, Operating Systems.}}
  \end{description}
\subsection[Bachelor of Technology, Information Technology]{\textsc{Bachelor of Technology, Information Technology} \hfill \textbf{8.01}}%
\small{Government College of Technology, Coimbatore} \hfill \small{May, 2010}

\datedsection{Graduate Research Project}{Jan 2016 to Present}
  \begin{description}
    \item[Kernel based approaches for Change point detection]  Finding change points in EEG signal data using kernel engineered towards exploiting the spatial relationship between EEG electrodes.  This will help in developing better Brain Computer Interface (BCI) applications.\\
      \textit{I am working with Prof\@. Zaid Harchaoui from NYU CILVR lab on this project}
  \end{description}

\section{Academic Projects}
  \begin{description}
    \item[Political opinion generator] --- Generate the summary of the opinions of political candidates by crawling news web sites. To be built using Apache Nutch, Lucene and Scikit-learn. (Ongoing project)
    \item[Grasp \& Lift EEG Detection] --- Multiclass classification of a person's hand action using EEG signal information.  Built using custom and scikit-learn's components.
      \par \textit{Dataset size:} \textasciitilde{}4G.  \textit{Feature Representation:} Vlad \& BOW\@.  \textit{Models:} Linear \& Gaussian SVM\@.
    \item[Liver \& Kidney cancer classifier] --- Identify the best biomarker for cancer between DNA Methylation and Protein Expression by using binnary classification on unbalanced data.
      \par \textit{Dataset size:} \textasciitilde{}20G.  \textit{Feature Representation:} PCA of original features.  \textit{Models:} Linear \& Gaussian SVM\@, Logistic Regression, Adaboost, Gaussian Naive Bayes.
    \item[Music Recommendation System] --- Recommender built by using a song's audio features.
      \par \textit{Dataset size:} \textasciitilde{}300G.  \textit{Feature Representation:} Vlad, BOFW, Mean vectors.  \textit{Models:} Linear \& Gaussian SVM, Logistic Regression.
    \item[Exploratory analysis of Taxi mobility and events] --- First step in finding the Most happening places in NYC\@.  Implemented Python Spark map \& reduce, and Hive.
      \par \textit{Dataset size:} \textasciitilde{}30G. \textit{Feature Representation:} Taxi rides grouped by zipcode and time slices.  \textit{Models:} Moving averages and then finding correlations.
  \end{description}

\datedsection{Employment}{Jul 2010 to Jan 2015}

\datedsubsection{Freelance Software Developer}{Nov 2013 to Jan 2015}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Worked as a full-stack developer on Vera, app.urblotter.com and `Today in History' iphone App.
  \item Quirl.com Performance Optimizations --- Load time: \textasciitilde10 sec \( \rightarrow \) 1 sec.  
    Asset size: \textasciitilde1.5Mb \( \rightarrow \) \textasciitilde600Kb.
  \item Setup the Quirl application architecture \& development process. Mentored the development team.
\end{itemize}
\datedsubsection{Founding Member, F1circle.com}{Jan 2013 to Oct 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built the complete application from scratch. \textbf{(ROR, Angularjs, Redis, Memcached, Mysql)}
  \item Built \textbf{Intellibox --- Information extraction engine} for extracting details from user posts.
\end{itemize}
\datedsubsection{Software Engineer, Insideview Inc}{Oct 2011 to May 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built an award winning \textbf{Company recommendation engine} in Insideview Hackaton 2012.
  \item Developed ActivityStream (Cassandra \& SimpleDB) and notifification framework (Drools \& Lucene).
\end{itemize}
\datedsubsection{Software Engineer, United Online Inc.}{Jul 2010 to Sep 2011}
\raggedright{\-\hspace{0.5cm}Built a \textbf{RPC} framework for spam filtering.  Automated day-to-day tasks using Perl scripts.}
\end{document}
