\documentclass{resume}
\usepackage{hyperref}

\begin{document}

\noindent{Anirudhan J Rajagopalan \hfill \url{https://github.com/rajegannathan}}\\
{\href{mailto:anirudhan@rajegannathan.in}{\nolinkurl{anirudhan@rajegannathan.in}} \hfill \url{https://www.linkedin.com/in/rajegannathan}}\\
{+1-- (646)-436 -3808 \hfill \url{http://stackoverflow.com/users/846970/anirudhan-j}}

\section{Education}
\noindent \hangindent=0em \hangafter=0 \textbf{MS}, Computer Science, Courant Institute of Mathematical Sciences, New York University. --- CGPA\@: 3.75 --- Expected Jan, 2016\\
\noindent \hangindent=0em \hangafter=0 \textbf{B.Tech}, Information Technology, Anna University, GCT, Coimbatore. --- CGPA\@: 8.0 --- May 2010.

\subsection{Graduate Course List}
Foundations of Machine Learning, Computational Machine Learning, Fundamental Algorithms, Operating Systems, Realtime \& Big-data Analytics, Financial Computing.

\datedsection{Employment}{4 years, 6 months}
\datedsubsection{.Net Developer --- NYU Opportunities}{Jul 2015 to Present}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Responsible for \textbf{computerizing} the complete workflow of the NYU Opportunities Program.
\end{itemize}

\datedsubsection{Freelance Software Developer}{Nov 2013 to Jan 2015}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Implemented the common sign-on page, branding workflows and modal framework for Vera.
  \item Built Urblotter (app.urblotter.com) a betting website for FIFA 2014. \textbf{(ROR, Angularjs, Sidekiq)}.
  \item Built a scrapper and admin app for `\textit{Today in History}' iphone app. --- \url{http://git.io/vZysq}
  \item Gre---flashcards: GRE preparation \textbf{android} app using Wordnik API\@. --- \url{http://git.io/vZ95e}
\end{itemize}
\datedsubsection{Consultant, Canvera Technologies}{Jan 2014 to Oct 2014}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built high performance responsive lightbox/slideshow with load more \& thumbstrips \textbf{(Angularjs)}.
  \item Performance Optimizations --- Load time: \textasciitilde10 sec \( \rightarrow \) 1 sec.  
    Asset size: \textasciitilde1.5Mb \( \rightarrow \) \textasciitilde600Kb.
  \item Built a rails like asset pipeline using \textbf{Grunt} and made the application production ready.
  \item Setup the application architecture \& development process. Mentored the development team.
\end{itemize}
\datedsubsection{Founding Member, F1circle.com}{Jan 2013 to Oct 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item F1circle.com is a bulletin board for professionals.
  \item Built the complete application from scratch. \textbf{(ROR, Angularjs, Memcached, Redis, Mysql)}
  \item Built Information extraction engine. It extracts name, place, \& price info from user's posts.
\end{itemize}
\datedsubsection{Software Engineer, Insideview Inc}{Oct 2011 to May 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built an award winning Company recommendation engine in Insideview Hackaton 2012. \textbf{(Java)}
  \item Improved the performance by 50\% for Insideview connections feature. \textbf{(Java, J2EE)}
  \item Developed in-product notification framework using \textbf{Drools framework} \& \textbf{Lucene indexes}.
  \item Built the Activitystream security framework using \textbf{AWS Simpledb} and custom eventbus.
\end{itemize}
\datedsubsection{Software Engineer, United Online Inc.}{Jul 2010 to Sep 2011}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built a \textbf{RPC} framework for spam filtering.  Automated day-to-day tasks using \textbf{Perl} scripts.
\end{itemize}
 
\section{Academic Projects}
\begin{description}
  \item[infoquestgct.com] --- Infoquest 2010 webapp.  Used for user registration and online events. \textbf{(PHP)}
  \item[Online Judge] --- OPC judge similar to codeforces.com, spoj.com.  Used in Infoquest 2010. \textbf{(C)}
  \item[Real time desktop search] --- A GUI tool for fast linux desktop search.  \textbf{(C++, GTK)}
\end{description}

\end{document}
