\documentclass{resume}

\usepackage{array}
\usepackage{hyperref}
\usepackage{enumitem}

\newenvironment{nscenter}
 {\parskip=0pt\par\nopagebreak\centering}
  {\par\noindent\ignorespacesafterend}

\begin{document}

\noindent{Anirudhan Jegannathan. R \hfill \url{https://github.com/rajegannathan}}\\
{\href{mailto:anirudhan@rajegannathan.in}{\nolinkurl{anirudhan@rajegannathan.in}} \hfill \url{https://www.linkedin.com/in/rajegannathan}}\\
{\url{http://rajegannathan.in} \hfill \url{https://odesk.com/users/~01d50700accaa363ea}}

\section{Education}
\begin{tabular}{>{\centering\arraybackslash}p{1in}l}
  B. Tech & \textbf{First class with Distinction}, Information Technology\\
  \small{(2006--2010)} & Govenrment College of Technology, Coimbatore.\\
    & GPA:\@ 7.99/10
\end{tabular}

\section{Awards \& Honours}
  \begin{itemize}[label={$\ast$}]
    \item \textbf{First Prize} in Insideview Hackaton for Company Recommendation Engine.\hfill Aug--2012\\
      \small{Built using \textit{N-Nearest Neighbour} algorithm.  Total of 25+ teams participated.}
    \item \textbf{First prize} in Project Presentation at Srishti 09, PSG Tech. \hfill Feb--2009\\
      \small{Built \textit{Real-time Desktop search for linux.} Srishti draws 3000+ participants every year.}
    \item \textbf{Second prize} in Project Presentation at Soft Sem Quiz (SSQ). \hfill Feb--2009\\
      \small{For \textit{SMS Simulator} and Algebric expression parser. SSQ is intra-college tech event.}
    \item \textbf{First prize} in district level Mathematics olympiad. \hfill Feb--2009\\
      \small{Twenty two teams participated in the final quiz on \textit{Calculas, Trignometr \& other High school syllabus}}
  \end{itemize}

\section{Undergraduate Project}
\begin{tabular}{l p{5.6in}}
  Title & \textbf{An endcient key management protocol with robust continuity for wireless sensor networks.}\\
  Guide & Dr. K. Baskaran, M.E. Ph.D.\\
        & A modified version of the Blom's scheme for efficient key management in Wireless Sensor Networks (WSN) is proposed.  This uses a hashing like algorithm along with modified Blom's key approach for securing key information with scalable key size.
\end{tabular}

\section{Noteworthy Projects}
\begin{description}
  \item[Gre wordcards] --- An android app for helping my GRE preparation.  Uses \textit{Wordnik} API to fetch details of entered words.  Avoids distraction by opening in full screen and hiding notification from other apps. Optimized for single hand use.  Prefetches \& caches word details when a user browses through the list.
  \item[Information Extraction system] --- The engine used to extract name, place and price info of ads in \url{f1circle.com}.  Normalizes and converts words to standard form and checks with dictionary of places and products to extract location \& product info.  Checks context of numbers to find price info.
  \item[Company Recommendation Engine] --- Recommends companies to sales person based on his previous history.  Built using \textit{user-user} similarity. Each company represented as a vector of 12 dimensions.  Percentage of views of a company by a person determines his past behaviour.
  \item[infoquestgct.com] --- The official website of Infoquest 2010. Developed user registration, virtual stock market, Online programming contest, online treasure hunt and custom captchas.
  \item[Online Judge] --- Judge for evaluating submitted programs.  Had customizable memory, file, process and time limits.
  \item[Real time desktop search] --- A gui tool for fast desktop search.  Uses watch descriptor to detect file system changes.
  \item[SMS Simulator] --- A network chat app with t9 dictionary implemented using trie.
\end{description}

\datedsection{Employment}{4+ years}
\datedsubsection{Consultant, Canvera Technologies}{Jan 2014 to Present}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Setup the application architecture \& development process. Mentored the development team.
  \item Built high performance lightbox/slideshow with dynamic image scaling, load more \& thumbstrips.
  \item Built a rails like asset pipeline using Grunt and made the application production ready.
  \item Performance Optimizations --- Load time: From \textasciitilde10 sec to 1 sec.  Asset size: From \textasciitilde1Mb to \textasciitilde600Kb.
\end{itemize}
\datedsubsection{Freelancer}{Nov 2013 to Present}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built Urblotter (app.urblotter.com) a betting website for FIFA 2014. (ROR, Angularjs, Sidekiq).
  \item Built a wikipedia parser and admin app for Today in History iphone app. (ROR, Nokogiri, Redis, Angularjs, Sidekiq, Mysql) --- \url{github.com/rajegannathan/wikipedia-scrapper}
  \item Built Gre---flashcards: My GRE preparation android app using Wordnik API\@.
\end{itemize}
\datedsubsection{Founding Member, F1circle.com}{Jan 2013 to Oct 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Built the complete application from scratch. (ROR, Angularjs, Memcached, Redis, Sidekiq, Mysql)
  \item Built Information extraction engine. It extracts name, place, \& price info from user's posts.
  \item Played a major role in User acquisition, marketing and sales in addition to engineering. 
\end{itemize}
\datedsubsection{Software Engineer, Insideview Inc}{Oct 2011 to May 2013}
\begin{itemize} \itemsep1pt \parskip0pt
\parsep0pt
  \item Developed an award winning Company recommendation engine in Insideview Hackaton 2012.  Built a Geo-spatial search application in the second hackaton.
  \item Developed in-product notification framework using Drools framework \& Lucene indexes.
  \item Developed the Activitystream security framework using AWS Simpledb and using custom eventbus.
  \item Owned up Insideview's connections features and did a number of performance optimizations.
\end{itemize}
\datedsubsection{Software Engineer, United Online Inc.}{Jul 2010 to Sep 2011}
I worked on United Online's billing systems which dealt with financial data.  As onboarding project, I built a RPC framework which was later used with Bogo filter for spam detection in Netzero emails.

\section{Teaching Experience}
  \begin{itemize}[label={$\ast$}]
    \item As a Placement Representative, I have conducted numerous Technical \& Soft-skill sessions in my undergraduate class.
    \item Technical topics covered: \textit{C,C++, Data Structures, Operating Systems, Compiler Design and DBMS.}
  \end{itemize}

\section{Extra-curricular Activities}
  \begin{itemize}[label={$\ast$}]
    \item \textit{Company Seargent Major} of my College National Caded Corps. \textit{(2TN CTC NCC)}.
    \item \textit{Placement Representative} of my batch.
  \end{itemize}
  
\end{document}
